### 2022-03-04 paper/localpsf.tex
moved rational positive definite section to appendix
editing writing

Each point source $\delta_{x_i}$ in the Dirac comb is scaled by $1/V(x_i)$ so that the resulting scaled impulse responses within $\eta_k$ are comparable in magnitude. Note that we are not in danger of dividing by zero, because our ellipsoid packing procedure from Section \ref{sec:sample_point_selection} excludes $x_i$ from consideration as a sample point if $V(x_i)$ is smaller than a predetermined threshold. Without this scaling, the portion of $\phi_{x_i}$ outside of $E_{x_i}$, which we neglect, may overwhelm $\phi_{x_j}$ for a nearby point $x_j$ if $V(x_i)$ is much larger than $V(x_j)$.

@@

Note that $y - \mu(x) + \mu(x_i)$ is generally not a gridpoint of the mesh used to discretize the problem, even if $y$, $x$, and $x_i$ are gridpoints. Hence,
evaluating $\eta_b\left(y - \mu(x) + \mu(x_i)\right)$, requires determining which mesh cell contains $y - \mu(x) + \mu(x_i)$, then evaluating the relevant finite element basis functions on that mesh cell. Fortunately, the mesh cell containing $y - \mu(x) + \mu(x_i)$ was already determined as a side effect of querying the AABB tree of mesh cells when we checked whether $y - \mu(x) + \mu(x_i) \in \Omega$.

\subsubsection{Improved interpolation for symmetric operators}
\label{sec:symmetric_improvements}
If $\Aop$ is symmetric, impulse responses of $\Aop$ are also impulse responses of $\Aop^T$. Let $\{y_i\}_{i=1}^k$ be the $k$ nearest sample points to $y$, excluding points $y_i$ such that $x - \mu(y) + \mu(y_i) \notin \Omega$. We could form an alternative approximation of $\Phi(y,x)$ by performing the same interpolation as before, but with $x$ and $y$ taking opposite roles. We combine both of these interpolation schemes to improve the approximation accuracy at negligible additional cost. The two interpolation schemes are combined by placing function values 
\begin{equation*}
\left(\widehat{f}_x\right)_i := \frac{V(x)}{V(x_i)}\phi_{x_i}\left(y - \mu(x) + \mu(x_i)\right), \qquad i=1,\dots,k,
\end{equation*}
at the points $x_i-x$, placing function values
\begin{equation*}
\left(\widehat{f}_y\right)_i := \frac{V(y)}{V(y_i)}\phi_{y_i}\left(x - \mu(y) + \mu(y_i)\right), \qquad i=1,\dots,k,
\end{equation*}
at the points $y_i-y$, and interpolating the combination of these $2k$ points and values at zero.

@@

\section{Solving for rational function scalars}
\label{app:solve_rational_system}

>>>>

Each point source $\delta_{x_i}$ is scaled by $1/V(x_i)$ so that the resulting scaled impulse responses within $\eta_k$ are comparable in magnitude. Note that we are not in danger of dividing by zero, because our ellipsoid packing procedure from Section \ref{sec:sample_point_selection} excludes $x_i$ from consideration as a sample point if $V(x_i)$ is smaller than a predetermined threshold. Without this scaling, the portion of $\phi_{x_i}$ outside of $E_{x_i}$, which we neglect, may overwhelm $\phi_{x_j}$ for a nearby point $x_j$ if $V(x_i)$ is much larger than $V(x_j)$.

@@

Note that $y - \mu(x) + \mu(x_i)$ is generally not a gridpoint of the mesh used to discretize the problem, even if $y$, $x$, and $x_i$ are gridpoints. Hence,
evaluating $\eta_b\left(y - \mu(x) + \mu(x_i)\right)$ requires determining which mesh cell contains $y - \mu(x) + \mu(x_i)$, then evaluating finite element basis functions on that mesh cell. Fortunately, the mesh cell containing $y - \mu(x) + \mu(x_i)$ was already determined as a side effect of querying the AABB tree of mesh cells when we checked whether $y - \mu(x) + \mu(x_i) \in \Omega$.

\subsubsection{Improvement for symmetric operators}
\label{sec:symmetric_improvements}
If $\Aop$ is symmetric, impulse responses of $\Aop$ are also impulse responses of $\Aop^T$. Let $\{y_i\}_{i=1}^k$ be the $k$ nearest sample points to $y$, excluding points $y_i$ such that $x - \mu(y) + \mu(y_i) \notin \Omega$. We could form an alternative approximation of $\Phi(y,x)$ by performing the same interpolation as before, but with $x$ and $y$ taking opposite roles. We combine both of these interpolation schemes to improve the approximation accuracy at negligible additional cost. The two interpolation schemes are combined by placing function values 
\begin{equation*}
\left(\widehat{f}_x\right)_i := \frac{V(x)}{V(x_i)}\phi_{x_i}\left(y - \mu(x) + \mu(x_i)\right), \qquad i=1,\dots,k,
\end{equation*}
at the points $x_i-x$, placing function values
\begin{equation*}
\left(\widehat{f}_y\right)_i := \frac{V(y)}{V(y_i)}\phi_{y_i}\left(x - \mu(y) + \mu(y_i)\right), \qquad i=1,\dots,k,
\end{equation*}
at the points $y_i-y$, and using radial basis functions to interpolate the combination of these $2k$ points and values at zero.

@@

\subsection{Solving for rational function scalars}
\label{app:solve_rational_system}
